Statistical Machine Learning Models on A Bank Marketing dataset

### 2025-12-09 Slides.Rmd
My changes to slides

---
title: "Statistical Machine Learning Models on A Bank Marketing dataset"
author: "Sandra, Tigist, Mussa Hassen, Waddah"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---

>>>>

---
title: "Statistical Machine Learning Models on A Bank Marketing dataset"
author: "Sandra Afrifa, Tigist Kefelew, Mussa Hassen, Waddah"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---
